%-------------------------
% Rohit Kumar - Resume
% Target: Data Analyst | Analytics Engineer | Data Engineer
%-------------------------

%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{fontawesome}
\usepackage{verbatim}
\usepackage{titlesec}
\usepackage{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
%-----------------------------------------

\input glyphtounicode
\pdfgentounicode=1

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro}
\urlstyle{same}
%-----------------------------------------

%----------MARGIN OPTIONS-----------------
\pagestyle{fancy}
\fancyhf{}

\renewcommand{\headrulewidth}{0in}
\renewcommand{\footrulewidth}{0in}

\setlength{\tabcolsep}{0in}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in}
\addtolength{\textheight}{1.0in}

\raggedbottom{}
\raggedright{}
%------------------------------------------

%--------SECTIONING COMMANDS---------
\titleformat{\section}
  {\large\bfseries}{}
    {0em}{\color{black}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------

%--------REDEFINITIONS----------------
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\ULdepth}{2pt}
%-------------------------------------

%--------CUSTOM COMMANDS--------------
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeSectionType}[3]{
  \item\begin{tabular*}{0.96\textwidth}[t]{
    p{0.16\linewidth}p{0.02\linewidth}p{0.81\linewidth}
  }
    \textbf{#1} & #2 & #3
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeTrioHeading}[3]{
  \item\small{
    \begin{tabular*}{0.96\textwidth}[t]{
      l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r
    }
      \textbf{#1} & \textit{#2} & #3
    \end{tabular*}
  }
}

\newcommand{\resumeQuadHeading}[4]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeQuadHeadingChild}[2]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\small#1} & {\small#2} \\
  \end{tabular*}
}

\newcommand{\resumeHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}
%-------------------------------------------


%__________________RESUME____________________
\begin{document}

%-----------CONTACT DETAILS------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Rohit Kumar \vspace{2pt}} & \\
  \small \raisebox{-0.1\height}\faPhone\ +91 8538938666  $|$
  \href{mailto:rohitkumar.me944@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rohitkumar.me944@gmail.com}} $|$
  \href{https://github.com/rohit-944}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/rohit-944}}
   $|$
  \href{https://linkedin.com/in/rohit944}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/rohit944}}
 & \\
\end{tabular*}
%--------------------------------------------


%-----------SUMMARY--------------------------
\section{Profile Summary}
\small{B.Tech CSE (AI) graduate with hands-on experience in SQL, Python, Power BI, and ETL pipeline development. Built end-to-end data projects covering EDA, dashboards, data modeling, and pipeline automation. Seeking Data Analyst / Analytics Engineer / Data Engineer roles to solve business problems with data.}

%--------------------------------------------
\section{Education}
  \resumeHeadingListStart{}
    \resumeQuadHeading{B.Tech Computer Science Engineering (AI Specialization) $|$ CGPA: 7.90}{Sep 2021 -- May 2025}
    {Audisankara College of Engineering and Technology}{Gudur, Andhra Pradesh}
  \resumeHeadingListEnd{}

%--------------SKILLS------------------------
\section{Technical Skills}
    \resumeItemListStart{}
     \resumeItem{\textbf{SQL:} Joins, Window Functions (ROW\_NUMBER, RANK, LAG/LEAD), CTEs, Subqueries, Aggregations, Query Optimization}
     
     \resumeItem{\textbf{Python:} Pandas, NumPy, Matplotlib, Seaborn, scikit-learn, Data Cleaning \& Transformation}

     \resumeItem{\textbf{BI \& Visualization:} Power BI (DAX, Power Query, Star Schema), Advanced Excel (VLOOKUP, Pivot Tables)}

     \resumeItem{\textbf{Data Engineering:} ETL Pipelines, Data Modeling, Schema Design, Data Warehousing Concepts}
     
     \resumeItem{\textbf{Databases:} PostgreSQL, MySQL, SQLite}
               
     \resumeItem{\textbf{Analysis:} EDA, KPI Analysis, RFM \& Cohort Analysis, Hypothesis Testing, A/B Testing Concepts}

     \resumeItem{\textbf{Tools:} Git, GitHub, Jupyter Notebook, DBeaver}
    \resumeItemListEnd{}
%--------------------------------------------


%-----------EXPERIENCE-----------------------
\section{Experience}
\resumeHeadingListStart{}
  \resumeQuadHeading{Data Analyst Intern}{Dec 2024 -- Apr 2025}
  {Council for Skills and Competencies (CSC India)}{Andhra Pradesh, India}
    \resumeItemListStart{}
      \resumeItem{Cleaned and preprocessed 10,000+ records using Python (Pandas, NumPy), reducing data inconsistencies by 40\%.}
      \resumeItem{Built 8+ visualizations using Matplotlib and Seaborn to identify revenue trends and customer segments.}
      \resumeItem{Performed EDA on sales datasets, uncovering 3 key business insights that informed reporting decisions.}
      \resumeItem{Implemented a classification model (scikit-learn) achieving 85\% accuracy on customer segmentation task.}
      \resumeItem{Collaborated with a team of 4 on data-driven projects, delivering weekly analysis reports to stakeholders.}
    \resumeItemListEnd{}

\resumeHeadingListEnd{}
%--------------------------------------------


%-----------PROJECTS--------------------------
\section{Projects}
  \resumeHeadingListStart{}

    \resumeTrioHeading
        {Retail Analytics Dashboard}
        {Python, SQL, Power BI, ETL}
        {\href{https://github.com/rohit-944/Retail_Analytics_Dashboard}{\underline{\textbf{GitHub}}}}
          \resumeItemListStart{}
            \resumeItem{Built an end-to-end ETL pipeline: extracted raw CSV data, transformed with Pandas, loaded into SQLite database.}
            \resumeItem{Designed normalized star schema and wrote advanced SQL queries for revenue trends and customer analysis.}
            \resumeItem{Performed RFM segmentation and cohort retention analysis to identify high-value customer segments.}
            \resumeItem{Developed interactive Power BI dashboard with 10+ KPIs, drill-through pages, and geographic insights.}
            \resumeItem{Analyzed \$1.4M revenue across 499 customers, delivering 5 actionable recommendations for growth.}
          \resumeItemListEnd{}

    \resumeTrioHeading
        {Sales Performance Dashboard}
        {Power BI, SQL, Excel, DAX}
        {\href{https://github.com/rohit-944/Sales_Performance_Dashboard}{\underline{\textbf{GitHub}}}}
          \resumeItemListStart{}
            \resumeItem{Built multi-page interactive Power BI dashboard analyzing sales trends across 4 regions and 50+ products.}
            \resumeItem{Wrote SQL queries to extract and transform raw sales data; created DAX measures for YoY growth and KPIs.}
            \resumeItem{Identified 3 underperforming regions contributing to 20\% revenue decline, enabling targeted interventions.}
            \resumeItem{Automated daily sales reporting workflow, reducing manual effort by 30\% (5 hours/week saved).}
          \resumeItemListEnd{}
            

  \resumeHeadingListEnd{}
%--------------------------------------------


%----------------CERTIFICATIONS----------------------
\section{Certifications}
  \resumeItemListStart{}

    \resumeItem{Data Analytics Job Simulation -- Deloitte (Forage) $|$
    \href{https://drive.google.com/file/d/18-UqFQCcVPAuZ6GHhrMMeC90eEm5NFfk/view?usp=sharing}{\underline{\textbf{Link}}}}
    
    \resumeItem{Databases and SQL for Data Science with Python -- IBM (Coursera) $|$    \href{https://www.coursera.org/account/accomplishments/verify/NO4KWV0K7SLY}{\underline{\textbf{Link}}}}
    
    \resumeItem{Python for Data Science, AI \& Development -- IBM (Coursera) $|$    \href{https://www.coursera.org/account/accomplishments/verify/N3WBHK7CEWXJ}{\underline{\textbf{Link}}}}
    
    \resumeItem{Data Visualization and Dashboards with Excel and Cognos -- IBM (Coursera) $|$    \href{https://www.coursera.org/account/accomplishments/verify/2R0E4QDSHV58}{\underline{\textbf{Link}}}}
 
  \resumeItemListEnd{}
%--------------------------------------------

\end{document}
